---
title: "Reproducibility Exercise"
output: pdf_document
---

This code organizes the data from CSV files into a data frame and creates new columns

Load the required package for reading data
```{r}
library(readr)
library(ggplot2)
library(stargazer)
```

1) Read the data into data frame
```{r}
data1 <- read_csv('inputs/gdp_52-67.csv')
data2 <- read_csv('inputs/le_52-67.csv')
```

2) Merge data frames based on continent, country, and year
```{r}
merged_df <- merge(data1, data2, by = c("continent", "country", "year"))
stargazer(merged_df, type = "text")
```

3) Create a new column with GDP per capita
```{r}
merged_df$gdpPercap <- merged_df$gdp / merged_df$pop
```

4) Visualize life expectancy and gdp per capita over time for Canada in the 1950s and 1960s using a line plot
```{r}
# Filter the data for Canada
canada_data <- merged_df[merged_df$country == "Canada", ]

# Create a line plot with two separate vertical axes
ggplot(data = canada_data, aes(x = year)) +
  geom_line(aes(y = lifeExp, color = "Life Expectancy"), size = 1) +
  geom_line(aes(y = gdpPercap / 180, color = "GDP per Capita"), size = 1) +
  
  # Primary y-axis for lifeExp
  scale_y_continuous(
    name = "Life Expectancy",
    sec.axis = sec_axis(trans=~.*180, name = "GDP per Capita")
  ) +
  
  # Customize colors
  scale_color_manual(values = c("Life Expectancy" = "blue", "GDP per Capita" = "red")) +
  
  # Set labels and title
  labs(
    x = "Year",
    y = "Life Expectancy",
    color = "Indicator",
    title = "Life Expectancy and GDP per Capita in Canada"
  ) +
  
  # Customize theme
  theme_minimal()
```

5) Regress life expectancy on gdp per capita and display the regression table
```{r}
# Fit a linear regression model
model <- lm(lifeExp ~ gdpPercap, data = merged_df)

# Display the regression table
stargazer(model, type = "text", style = "aer")
```


